---
title: "p8105_hw1_hn2453"
author: Huiyan Ni
date: 2024-09-21
output: github_document
---
```{r}
library(ggplot2)
library(tidyverse)
```

# Problem 1

## Import data from package palmerpenguins.
```{r}
data("penguins", package = "palmerpenguins")
```

## Description of the penguins dataset.

```{r}
head(penguins)
pen_variable = colnames(penguins)
pen_rows = nrow(penguins)
pen_cols = ncol(penguins)

mean_flipper_length = mean(penguins$flipper_length_mm, na.rm = TRUE)

```
From previous information, we can get penguins dataset have 8 variables: `r pen_variable`.

Penguins dataset have `r pen_rows` rows and `r pen_cols` columns. 

The mean flipper length is `r mean_flipper_length` mm. 

## Make scatterplot between bill_length_mm(x) and flipper_length_mm(y) and save the output plot.
```{r warning=FALSE}
plot1 <- ggplot(penguins,aes(x = bill_length_mm, y = flipper_length_mm, color=species)) + geom_point()

plot1

ggsave("scatterplot1.pdf",plot = plot1)
```

# Problem 2

## create the required data frame
```{r}
set.seed(1)

plot_df = tibble(
  x = rnorm(n=10),
  vec_x = x > 0,
  cha_vec = rep("sample",10),
  fac_vec = factor(sample(c("high","low","medium"), 10, replace = TRUE))
  
)

plot_df

```

## calculate the mean in plot_df
```{r}
x_vector = plot_df$x
x_mean = mean(x_vector)
x_mean
```

```{r}
vecx_vector = plot_df$vec_x
vecx_mean = mean(vecx_vector)
vecx_mean
```

```{r eval=FALSE}
cha_vector = plot_df$cha_vec
mean(cha_vector)
```


```{r eval=FALSE}
fac_vector = plot_df$fac_vec
mean(fac_vector)
```

The mean of x is `r x_mean`. The mean of vec_x is `r vecx_mean`. The mean of cha_vec and fac_vec cannot be calculated due to mean() only accept numeric and logical value. 

## convert variables from one type to another
```{r eval=FALSE}
numeric_vecx = as.numeric(vecx_vector)
numeric_vecx

numeric_cha = as.numeric(cha_vector)
numeric_cha

numeric_fac = as.numeric(fac_vector)
numeric_fac

```
When convert logical variables to numeric variables, the true will become to 1 and false will become to 0. This is why logical variables can use mean function. However, when convert character variables to numeric variables, it will become to NA. And when convert factor variables to numeric variables, it will become to some useless integers. 



