---
title: "p8105_hw1_hn2453"
author: Huiyan Ni
date: 2024-09-21
output: github_document
---
```{r}
library(ggplot2)
library(tidyverse)
```

#Problem 1

##Import data from package palmerpenguins.
```{r}
data("penguins", package = "palmerpenguins")
```

##Description of the penguins dataset.

```{r}
head(penguins)
pen_variable = colnames(penguins)
pen_rows = nrow(penguins)
pen_cols = ncol(penguins)

mean_flipper_length = mean(penguins$flipper_length_mm, na.rm = TRUE)

```
From previous information, we can get penguins dataset have 8 variables: `r pen_variable`.

Penguins dataset have `r pen_rows` rows and `r pen_cols` columns. 

The mean flipper length is `r mean_flipper_length` mm. 

##Make scatterplot between bill_length_mm(x) and flipper_length_mm(y) and save the output plot.
```{r warning=FALSE}
plot1 <- ggplot(penguins,aes(x = bill_length_mm, y = flipper_length_mm, color=species)) + geom_point()

plot1

ggsave("scatterplot1.pdf",plot = plot1)
```

#Problem 2

##create the required data frame
```{r}
set.seed(1)

plot_df = tibble(
  x = rnorm(n=10),
  vec_x = x > 0,
  cha_vec = rep("sample",10),
  fac_vec = factor(sample(c("one","two","three"), 10, replace = TRUE))
  
)

plot_df

```



